An Online Visual Loop Closure Detection Method for Indoor Robotic Navigation

### 2014-12-01 latex-spie/article.tex
almost finished

@@

The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from each other. The tests are done with either using gray and depth images separately or using both of them. After that, the difference matrices are calculated to examine the results. Nearest Neighbour (NN) algorithm is applied to classify the new locations using the $L_{1}$ distance metric. In addition to this, the last 100 frames are not included in the classification phase, because it the sensor is always moving and these frames correspond to the area behind the sensor.

The method described in Section \ref{sec:method} has basically two parameters that must be adjusted. One of them is $k\times k$ which defines the number of the subimages that the input image was partitioned to, and the other one is n, which is the order of the Zernike polynomials used. During the experiments, the selected parameters are $k = 30$ and $n = 2$. Then, the quantized $k\times k$-sized matrix obtained from the input image is divided into $5\times 5$ equal-sized non-overlapping subregions. The histograms of each subregion are simply concatenated to compose the feature vector of an image. In order to construct the ultimate feature vector containing both gray and depth images, each feature vector obtained from both images are also concatenated.

@@

In order to measure loop closing performance of the algorithm in different illumination levels, three different datasets are created in an indoor environment by using Kinect sensor which can grab both gray and depth images at the same time. The lighting conditions in the datasets are bright, dim and dark in which both depth and gray images are captured. The exemplary images belonging to different datasets are shown in Figure \ref{fig:dataset}. In some cases, the line of sight of the Kinect is not enough to capture the depth information for distances above $10m$. Thus, some of the depth images are unreliable.

@@

% BENCHMARK DATASETS
\begin{figure}[!htb]
        \centering

>>>>

% BENCHMARK DATASETS
\begin{figure}
        \centering

@@

The method implemented in this paper has been evaluated on three datasets which lighting conditions are different from each other. The tests are done with either using grayscale and depth images separately or using both of them. After that, the difference matrices are calculated to examine the results. Nearest Neighbour (NN) algorithm is applied to classify the new locations using the $L_{1}$ distance metric. In addition to this, the last 100 frames are not included in the classification phase, because it the sensor is always moving and these frames correspond to the area behind the sensor.

The method described in Section \ref{sec:method} has basically two parameters that must be adjusted. One of them is $k\times k$ which defines the number of the subimages that the input image was partitioned to, and the other one is n, which is the order of the Zernike polynomials used. During the experiments, the selected parameters are $k = 30$ and $n = 2$. Then, the quantized $k\times k$-sized matrix obtained from the input image is divided into $5\times 5$ equal-sized non-overlapping subregions. The histograms of each subregion are simply concatenated to compose the feature vector of an image. In order to construct the ultimate feature vector containing both grayscale and depth images, each feature vector obtained from both images are also concatenated.

@@

In order to measure loop closing performance of the algorithm in different illumination levels, three different datasets are created in an indoor environment by using Kinect sensor which can grab both grayscale and depth images at the same time. The lighting conditions in the datasets are bright, dim and dark in which both depth and grayscale images are captured. The exemplary images belonging to different datasets are shown in Figure \ref{fig:dataset}. In some cases, the line of sight of the Kinect is not enough to capture the depth information for distances above $10m$. Thus, some of the depth images are unreliable.

@@
